Scoring_questionnaires2021

### 2021-08-23 Questionnaires_scoring2021.Rmd
Update Questionnaires_scoring2021.Rmd

# read the files
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

@@

IQ
IQ: esh8
```{r}
IQ: esh8

@@

>>>>

# read the files
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}
library(readxl)
db_BPQ <- read_excel("data_exp_11458-v9_questionnaire-bbc4.xlsx")
View(data_exp_11458_v9_questionnaire_bbc4)

@@

IQ
IQ: esh8

345 to 356 need to be scores separatelly

Lucy: https://docs.google.com/spreadsheets/d/1P9x7oHxpUTanb412czfgYqR_stPJ3fHzwYiItANpfO8/edit#gid=277478937
```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8")

db_IQ <- list.files(pattern = "*-esh8.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

colnames(db_IQ)

db_IQ1<- select(db_IQ, c(1,13,16, 37,45:48))

db_IQ2<- subset(db_IQ1, !is.na(Response))
View(db_IQ2)

db_IQ3 <- db_IQ2%>%
  group_by(`Participant Private ID`, `Participant Completion Code`)%>%
  summarise_if(is.numeric, sum, na.rm = TRUE)

db_IQ3$Matrix_Total<- db_IQ3$Correct
db_IQ3$completion_code<- db_IQ3$`Participant Completion Code`

colnames(db_IQ3)
db_IQ4<- select(db_IQ3,c(1,7,6))

@@

Merge all into one self report

```{r}
db_demog$`Participant Completion Code`<- NULL

db_demog$completion_code<- db_demog$`Participant Completion Code`

left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS, by = "completion_code")

db_DASS4$`Participant Public ID`<-NULL

db_demog$`Event Index.x`<-NULL
db_DASS4$`Participant Private ID`<- NULL
db_AQ4$`Participant Private ID`<- NULL

db_BVAQ3$`Participant Private ID`<- NULL
db_IQ4$`Participant Private ID`<- NULL
db_BPQ3$`Participant Private ID`<- NULL

db_BPQ3

left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3, by = "completion_code")

db_self_rep<- Reduce(merge, list(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS))

# db_IAS$
```
